Discrete Quantum Theories and Computing

### 2019-02-22 dissertation.tex
dissertation.lyx Secs. 5.1.1, 5.1.2, and partial 5.1.3 Reviewed...

Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting subspace
of events, $\eventsC$, recovers the definition of classical IVPMs.
 To see this, we first define a subspace of events. $\events'$ is
called a \emph{subspace} of the set of events~$\events$ if $\events'$
contains the projectors $\mathbb{0}$ and $\mathbb{1}$ and is closed
under complements, sums, and products. In particular, for any projector
$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for each pair
of commuting projectors $P_{0}\in\events'$ and $P_{1}\in\events'$,
we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$. Given
a mutually commuting subspace~$\eventsC$ whose elements are diagonalizable
by a common orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
the function $\varphi\colon2^{\Omega}\rightarrow\events$ defined
in Eq.~(\ref{eq:pullback-function}) maps any set~$E$ to the sum
of the projectors formed by elements in $E$, and preserve all operations
used to define classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
and~(\ref{eq:pullback-properties}). According to the same reason
as the classical counterpart, Eq.~(\ref{eq:classical-pullback}),
given a QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}$, the
function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
defined by precomposition $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
is the pullback of $\bar{\mu}$ by $\varphi$ and is a classical IVPM
naturally.

Since we can pull back a QIVPM to a classical one, known properties
of classical IVPMs directly hold for QIVPMs when one restricts to
mutually commuting events~$\eventsC$, and one of them is \emph{core}.
Recall in Sec.~\ref{subsec:Definitions-of-IVPMs}, given a classical
IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ and an event
$E\subseteq\Omega$ such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$
and $\bar{\mu}\left(\overline{E}\right)=\left[0.7,0.8\right]$, we
discussed the ``true'' probabilities, $\mu\left(E\right)$ and $\mu\left(\overline{E}\right)$,
can be anywhere in the range $\left[0.2,0.3\right]$ and $\left[0.7,0.8\right]$,
respectively, as long as they satisfy $\mu\left(E\right)+\mu\left(\overline{E}\right)=1$.
These ``true'' probabilities can be represented as a probability
measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ satisfying
\begin{align}
\mu\left(E\right) & \in\left[0.2,0.3\right]=\bar{\mu}\left(E\right)\,, & \mu\left(\overline{E}\right) & \in\left[0.7,0.8\right]=\bar{\mu}\left(\overline{E}\right)\,.
\end{align}
Together with the trivial fact
\begin{align}
\mu\left(\emptyset\right) & =0\in\imposs=\bar{\mu}\left(\emptyset\right)\,, & \mu\left(\Omega\right) & =1\in\necess=\bar{\mu}\left(\Omega\right)\,,
\end{align}
we conclude the ``true'' probability of each event belongs to the
interval probability of the corresponding event. This conclusion gives
the following definition of core.

@@

Like how we pulled back classical ideas to the quantum world in Secs.~\ref{subsec:Definitions-of-IVPMs}
and~\ref{subsec:States-Consistent-with-IVPMs}, we start from defining
the classical expectation value relative to IVPMs. Consider a classical
IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ and an event
$E\subseteq\Omega$ such that 
\begin{align}
\bar{\mu}\left(E\right) & =\left[0.2,0.3\right]\,, & \bar{\mu}\left(\overline{E}\right) & =\left[0.7,0.8\right]\,,\label{eq:IVPM_example}
\end{align}
and a random variable $X\colon\Omega\rightarrow\mathbb{R}$ defined
by
\begin{equation}
X\left(\omega\right)=\begin{cases}
1 & \textrm{if }\omega\in E\,;\\
2 & \textrm{if }\omega\notin E\,.
\end{cases}\label{eq:random_variable_example}
\end{equation}
As we have discussed, the ``true'' probability is a probability
measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ consistent
with $\bar{\mu}$ on every event. On one extreme case, $\mu\left(E\right)=0.2$,
the expectation value of $X$ relative to $\mu$ is 
\begin{equation}
1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,.
\end{equation}
On the other extreme case, $\mu\left(E\right)=0.3$, the expectation
value of $X$ relative to $\mu$ is
\begin{equation}
1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
\end{equation}
In other words, if $\mu$ is in the core of $\bar{\mu}$, the expectation
value of $X$ belongs to $\left[1.7,1.8\right]$ which should be the
expectation value of $X$ with respect to $\bar{\mu}$.

>>>>

Our definition of QIVPMs is consistent with classical IVPMs in the
sense that a restriction of QIVPMs to mutually commuting subspace
of events~$\eventsC$ recovers the definition of classical IVPMs.
 To see this, we first define a subspace of events: $\events'$ is
called a \emph{subspace} of the set of events~$\events$ if $\events'$
contains the projectors $\mathbb{0}$ and $\mathbb{1}$ and is closed
under complements, sums, and products. In particular, for any projector
$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for each pair
of commuting projectors $P_{0}\in\events'$ and $P_{1}\in\events'$,
we have $P_{0}P_{1}$ and $P_{0}+P_{1}-P_{0}P_{1}\in\events'$. Given
a mutually commuting subspace~$\eventsC$ whose elements are diagonalizable
by a common orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
the function $\varphi\colon2^{\Omega}\rightarrow\events$ defined
in Eq.~(\ref{eq:pullback-function}) maps any set~$E$ to the sum
of the projectors formed by elements in $E$, and preserve all operations
used to define classical and quantum IVPMs as in Eqs.~(\ref{eq:pullback-properties-basic})
and~(\ref{eq:pullback-properties}). According to the same reason
as the classical counterpart, Eq.~(\ref{eq:classical-pullback}),
given a QIVPM~$\bar{\mu}\colon\events\rightarrow\mathscr{I}$, the
function $\varphi^{*}\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$
defined by precomposition $\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\bar{\mu}\left(\varphi\left(E\right)\right)$
is the pullback of $\bar{\mu}$ by $\varphi$ and is a classical IVPM
naturally.

Since we can pull back a QIVPM to a classical one, known properties
of classical IVPMs directly hold for QIVPMs when one restricts to
mutually commuting events~$\eventsC$, and one of them is \emph{core}.
Recall in Sec.~\ref{subsec:Definitions-of-IVPMs}, given a classical
IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ and an event
$E\subseteq\Omega$ such that $\bar{\mu}\left(E\right)=\left[0.2,0.3\right]$
and $\bar{\mu}\left(E\right)=\left[0.7,0.8\right]$, we discussed
the ``true'' probabilities, $\mu\left(E\right)$ and $\mu\left(\overline{E}\right)$,
can be anywhere in the range $\left[0.2,0.3\right]$ and $\left[0.7,0.8\right]$,
respectively, as long as they satisfy 
\begin{equation}
\mu\left(E\right)+\mu\left(\overline{E}\right)=1\,.\label{eq:total-probability}
\end{equation}
Eq.~(\ref{eq:total-probability}) guarantees the function mapping
an event to its ``true'' probabilities, $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$,
is a probability measure. Requiring the ``true'' probability of
each event should be in the range spanned by the interval-valued probability
of the same event, i.e., 
\begin{align}
\mu\left(E\right) & \in\left[0.2,0.3\right]=\bar{\mu}\left(E\right)\,, & \mu\left(\overline{E}\right) & \in\left[0.7,0.8\right]=\bar{\mu}\left(\overline{E}\right)\,,\\
\mu\left(\emptyset\right) & =0\in\imposs=\bar{\mu}\left(\emptyset\right)\,, & \mu\left(\Omega\right) & =1\in\necess=\bar{\mu}\left(\Omega\right)\,,
\end{align}
gives the following definition of core.

@@

Like how we pulled back classical ideas to the quantum world in Secs.~\ref{subsec:Definitions-of-IVPMs}
and~\ref{subsec:States-Consistent-with-IVPMs}, we start from defining
the classical expectation value relative to IVPMs. Consider a classical
IVPM $\bar{\mu}\colon2^{\Omega}\rightarrow\mathscr{I}$ and an event
$E\subseteq\Omega$ such that 
\begin{align}
\bar{\mu}\left(E\right) & =\left[0.2,0.3\right]\,, & \bar{\mu}\left(\overline{E}\right) & =\left[0.7,0.8\right]\,,\label{eq:IVPM_example}
\end{align}
and a random variable $X\colon\Omega\rightarrow\mathbb{R}$ defined
by
\begin{equation}
X\left(\omega\right)=\begin{cases}
1 & \textrm{if }\omega\in E\,;\\
2 & \textrm{if }\omega\notin E\,.
\end{cases}\label{eq:random_variable_example}
\end{equation}
As we have discussed, the ``true'' probability is a probability
measure $\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$ consistent
with $\bar{\mu}$ on every event. On one extreme case, $\mu\left(E\right)=0.2$,
the expectation value of $X$ relative to $\mu$ is 
\begin{equation}
\int X\rmd\pmeas=1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,.
\end{equation}
On the other extreme case, $\mu\left(E\right)=0.3$, the expectation
value of $X$ relative to $\mu$ is
\begin{equation}
\int X\rmd\pmeas=1\cdot\mu\left(E\right)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
\end{equation}
In other words, if $\mu$ is in the core of $\bar{\mu}$, the expectation
value of $X$ relative to $\mu$, $\int X\rmd\pmeas$, belongs to
$\left[1.7,1.8\right]$ which should be the expectation value of $X$
relative to $\bar{\mu}$.
